---
title: "Cabbages"
author: "Aubrey Garcia!"
date: "05-21-24"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods? 
$H_0$: There is no difference in the average vitamin C content of cabbages based on cultivation method.

$H_A$: There is a difference in the average Vitamin C content of cabbeges based on cultivated methods

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

Vitamin C is numerical, cultivation is categorical.


numerical-categorical
Numerical~cat Help file so we use Numerical~cat Help file

# Results
```{r}
boxplot(VitC~Cult,data=veggy)
```
<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

Cultivation method C52 has more vitamin C than cultivation method C39

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

```{r}
favstats(VitC~Cult,data=veggy)
```
The numerical summery shows that cultivation C52 is higher, with a mean of 64.4 , than the c39 cultivation with a averages of 51.5, which goes to show that c52 would be a better option for cabbages.



<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```
The P vaule is 0.00000003405, that the number is way below .5(p-value), so small that we will reject the null hypothesis.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Originally the question was  whether there was a difference in average VitC between c39 and c52 cultivation methods? The null hypothesis stated that There is no difference in the average vitamin C content of cabbages based on cultivation method. While the Alternative Hypothesis stated that There is a difference in the average Vitamin C content of cabbages based on cultivated methods. After much statistical testing, the null hypothesis was untimely rejected. The numerical summary shows that cultivation C52 is higher, with a mean of 64.4 , than the c39 cultivation with a averages of 51.5, which goes to show that c52 would be a better option for cabbages. As well as, in the Welch Two Sample t-test, results showed, t = -6.3909, df = 56.376, p-value =  0.0000000345. Thus the P-value being less than .5, the null hypothesis is rejected and c52 is the best cultivation method for cabbage. 
